Going from coarse landings data to fine scale species distribution

### 2022-05-05 Version_M2_plusieurszones/draft/paper_3/paper_3.Rmd
WIP

@@

The original model proposed in  @alglave_combining_2022 is defined at the individual catch scale, those catch are  derived from the catch declaration combined with the VMS data. This is classically done in fisheries science REFREFEREFREF by using a uniform reallocation process. This process consists in counting, for a given vessel, on a given day,  the number $m_j$ of fishing points in $\mathcal{A}_j$ and define for each $x_i\in\mathcal{A}_j,$, the associated individual catch $Y(x_i)=D_j/m_j$. As a direct consequence, the so reconstructed individual catch are similar to a Catch Per Unit of Effort (CPUE), effort being measure in hours. As noted by @alglave_combining_2022, this process has several drawbacks.
First, as a consequence of the reallocation process, the so reconstructed individual catches tend to exhibit smoother pattern than the original catches. Second, the actual number of data is the total number of declaration while the number of data after the reallocation process is the number of fishing locations, which is approximately 10 times the number of declarations. From a statistical point of view, this overestismation of the number of informative data tends to produce excessively narrow confidence intervals.

@@

To circumvent such limitations, we propose an alternative approach that models the catch declarations $D_j$ instead of the individual catch $Y(x_i)$. As we  aim to propose a model compatible with the original one, we are lead to specify  the distribution of $D_j$ which consists of a sum of $m_j$ random variables folowwing a mixture distribution. This distribution has no  known analytical form. However the catch data also exhibit some zero inflation and a skewed repartition of the values and a mixture model would be a good candidate.  Theefore, we propose to model $D_j$ as a mixture between a Dirac mass in $0$ and a lognormal distribution. In order to compare the original approach with our proposition, we define the different key quantities, i.e  the mixture proportion, the expected positive catch declaration and its variance so that to match the original propostion:

>>>>

\begin{equation}
\label{eq:defY}
Y_i | S(x_i)  \overset{ind}{\sim} \M{p_i}{\frac{S(x_i)}{1-p_i}}{\sigma^2}
\end{equation}

@@

The original model proposed in  @alglave_combining_2022 is defined at the individual catch scale, those catch are  derived from the catch declaration combined with the VMS data. This is classically done in fisheries science REFREFEREFREF by using a uniform reallocation process. This process consists in counting, for a given vessel, on a given day,  the number $m_j$ of fishing points in $\mathcal{A}_j$ and define for each $x_i\in\mathcal{A}_j,$ the associated individual catch $\Yr(x_i)\defeq D_j/m_j$. As a direct consequence, the so reconstructed individual catch are similar to a Catch Per Unit of Effort (CPUE), effort being measure in hours. As noted by @alglave_combining_2022, this process has several drawbacks.
First, as a consequence of the reallocation process, the reconstructed individual catches tend to exhibit smoother pattern than the original catches. Second, the actual number of data is the total number of catch declaration while the number of data after the reallocation process is the number of fishing locations, which is approximately 10 times the number of declarations. From a statistical point of view, this overestismation of the number of informative data tends to produce excessively narrow confidence intervals.

@@

To circumvent such limitations, we propose an alternative approach that models the catch declarations $D_j$ instead of the reconstructed individual catch $\Yr(x_i)$. As we  aim to propose a model compatible with the original one, we are lead to specify  the distribution of $D_j$ which consists of a sum of $m_j$ random variables following a mixture distribution. This distribution has no  known analytical form. However the catch declaration data also exhibit some zero inflation and a long tail repartition of the values: a mixture model would be a good candidate. Therefore, we propose to use the same family of distribution for  $D_j$ than the one use for $\Yr$: a mixture between a Dirac mass in $0$ and a lognormal distribution. This is not exact, as the distribution of $D_j$ should be defined as convolution of mixtures but would result in quite untractable model. We somehow approximate the sum of  the original mixture distributions  by a mixture distribution of the same kind and we define the different key quantities, i.e  the mixture proportion, the expected positive catch declaration and its variance so that to match the original propostion:
